Conditional selectivity for triplestores

### 2012-09-18 conditional/trunk/selectivity-basic.tex
add todo
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@379 43ef1190-90fd-4dd7-a769-d0121f02b80e

The above are the parts of the equations that can be computed directly
from the VoID description, and in the next section we shall see how
they can be exploited most efficiently.

@@

This case is similar to the above, and we can write 
\begin{equation}\label{eq:selsuunobpb}
\sel{T_{\{s~p~?\}}} = \sel{O = ? | P = p \cap S = s} \cdot 
\sel{S = s | P = p} \cdot
\sel{P = p} . 
\end{equation}
We note that we can't find the first two parts in the VoID
description, but we also note with interest that the first part shows
that only the marginal distribution of objects is needed to estimate
this part.

>>>>

The above are the parts of the equations that can be computed directly
from the VoID description, and in the next section we shall see how
they can be exploited.

@@

This case is similar to the above, and we can write 
\begin{equation}\label{eq:selsuunobpb}
\sel{T_{\{s~p~?\}}} = \sel{O = ? | P = p \cap S = s} \cdot 
\sel{S = s | P = p} \cdot
\sel{P = p} . 
\end{equation}
We note that we can't find the first two parts in the VoID
description\todo{2nd part always 1?}, but we also note with interest that the first part shows
that only the marginal distribution of objects is needed to estimate
this part.
